### 2017-11-16 manuscript.rmd
spelling

	# The threshold of allowed fractional devience of node age from clade age
	age_window = 0.1

@@

We next approximated the Phylogenetic Independent Contrasts for the the genes that have $\Delta$AIC less than the threshold for OU under an OU model. These analyses do not reject the null hypothesis (Wilcoxon $P=`r  wilcox_ou %>% round( 3 )`$). The challenge with such an analysis is that BM is intrinsic to the classic implementation of Phylogenetic Independent Contrasts, which use the fact that the expected variance is proportional to branch length to scale each contrast. Under OU, branch length no longer has a linear relationship to expected variance. We therefore took an alternative simulation-based approach to scaling the OU contrasts. We implemented this new method, which we call picx (for "pic extended models"), in our R package hutan (https://github.com/caseywdunn/hutan). For each tree, picx first estimate the model parameters from the observed data. It then simulates two hundred datasets under these parameters, recording both the internal and tip node states. It then scales the observed contrasts by the mean magnitude of the corresponding contrasts in the simulations. We validated the method by comparing picx BM results to the standard pic results calcualted by ape. These validations indicated a strong linear realationship between the two ($R^2$ > 0.95). This approach could be extended to approximate Phylogenetic Independent Contrasts under other continuous models of evolution as well.

>>>>

	# The threshold of allowed fractional deviance of node age from clade age
	age_window = 0.1

@@

We next approximated the Phylogenetic Independent Contrasts for the the genes that have $\Delta$AIC less than the threshold for OU under an OU model. These analyses do not reject the null hypothesis (Wilcoxon $P=`r  wilcox_ou %>% round( 3 )`$). The challenge with such an analysis is that BM is intrinsic to the classic implementation of Phylogenetic Independent Contrasts, which use the fact that the expected variance is proportional to branch length to scale each contrast. Under OU, branch length no longer has a linear relationship to expected variance. We therefore took an alternative simulation-based approach to scaling the OU contrasts. We implemented this new method, which we call picx (for "pic extended models"), in our R package hutan (https://github.com/caseywdunn/hutan). For each tree, picx first estimate the model parameters from the observed data. It then simulates two hundred datasets under these parameters, recording both the internal and tip node states. It then scales the observed contrasts by the mean magnitude of the corresponding contrasts in the simulations. We validated the method by comparing picx BM results to the standard pic results calculated by ape. These validations indicated a strong linear relationship between the two ($R^2$ > 0.95). This approach could be extended to approximate Phylogenetic Independent Contrasts under other continuous models of evolution as well.
